El rol de la familia y la escuela en la socialización política de las actitudes

### 2022-09-02 paper.Rmd
Actualización tablas en función de los comentarios de Diane

coef_names <- c(
          "Intercept",
          "Girl (Ref. Boy)",
          "ISCED level 2 o 3 (Ref. ISCED level 1 or less)",
          "ISCED level 4",
          "ISCED level 5 or more",
          "Between 11 and 25 books (Ref. between 0 and 10 books)",
          "Between 26 and 100 books",
          "More than 100 books",
          "Quintile 2 (Ref. Quintile 1)",
          "Quintile 3",
          "Quintile 4",
          "Quintile 5",
          "Do not know / Not answer"
          )
omit_coef <- "(dependencia)|(REGION)|(c_civic)"
footnote<- "\\item %stars. \\item All models are controlled for region of residence (p>0.05), administrative dependency of the school (p>0.05) and level of civic knowledge of the student ($p$<0.05)"
scale_box <- 0.825
```

@@

```{r, echo=FALSE, results='asis'}
caption <- "Multilevel Regression Model for Parents attitudes"
knitreg(list(h4_igualdad.apod,h4_esp_pub.apod,h4_esp_priv.apod), 
        custom.model.names = c(
          "Equal Rights and Opportunities",
          "Equal Distribution in public sphere",
          "Equal Distribution in private sphere"
        ), 
        custom.note = "$***p <$ 0.001, $**p <$ 0.01, $*p <$ 0.05",  
        custom.coef.names = c(
          "Intercept",
          "ISCED level 2 o 3 (Ref. ISCED level 1 or less)",
          "ISCED level 4",
          "ISCED level 5 or more",
          "Between 11 and 25 books (Ref. Between 0 and 10 books)",
          "Between 26 and 100 books",
          "More than 100 books",
          "Quintile 2 (Ref. Quintile 1)",
          "Quintile 3",
          "Quintile 4",
          "Quintile 5",
          "Missing",
          "Reg. of Maule (Ref. Reg. of Antofagasta)",
          "Reg. Metropolitana"
        ),
       scalebox = scale_box,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```

>>>>

coef_names <- c(
          "Intercept",
          "Girl (Ref. Boy)",
          "ISCED level 2 o 3 (Ref. ISCED level 1 or less)",
          "ISCED level 4",
          "ISCED level 5 or more",
          "Between 11 and 25 books (Ref. between 0 and 10 books)",
          "Between 26 and 100 books",
          "More than 100 books",
          "Quintile 2 (Ref. Quintile 1)",
          "Quintile 3",
          "Quintile 4",
          "Quintile 5",
          "Do not know / No answer"
          )
omit_coef <- "(dependencia)|(REGION)|(c_civic)"
footnote<- "\\item %stars. \\item All models are controlled for region of residence (p>0.05), administrative dependency of the school (p>0.05) and level of civic knowledge of the student ($p$<0.05)"
scale_box <- 0.825
```

@@

```{r, echo=FALSE, results='asis'}
caption <- "Multilevel Regression Model for Parent Attitudes"
knitreg(list(h4_igualdad.apod,h4_esp_pub.apod,h4_esp_priv.apod), 
        custom.model.names = c(
          "Equal Rights and Opportunities",
          "Equal Distribution in public sphere",
          "Equal Distribution in private sphere"
        ), 
        custom.note = "$***p <$ 0.001, $**p <$ 0.01, $*p <$ 0.05",  
        custom.coef.names = c(
          "Intercept",
          "ISCED level 2 o 3 (Ref. ISCED level 1 or less)",
          "ISCED level 4",
          "ISCED level 5 or more",
          "Between 11 and 25 books (Ref. Between 0 and 10 books)",
          "Between 26 and 100 books",
          "More than 100 books",
          "Quintile 2 (Ref. Quintile 1)",
          "Quintile 3",
          "Quintile 4",
          "Quintile 5",
          "Missing",
          "Reg. of Maule (Ref. Reg. of Antofagasta)",
          "Reg. Metropolitana"
        ),
       scalebox = scale_box,
       caption.above = T,
       caption=caption,
       float.pos="h!"
       )
```
